%-------------------------
% Resume in Latex
% Author : Ethan Conner
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\setlength{\footskip}{4.08003pt}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
  \begin{itemize}[leftmargin=0.15in, label={}, topsep=-3pt, itemsep=-3pt]
}
\newcommand{\resumeSubHeadingListEnd}{
  \end{itemize}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \textsc{Ethan Conner}} \\ \vspace{1pt}
    \small 682-208-6226 $|$ \href{mailto:ethanjacobconner@gmail.com}{\underline{ethanjacobconner@gmail.com}} $|$ \href{https://github.com/EJ-Conner}{\underline{github.com/EJ-Conner}}
\end{center}


%-----------EXPERIENCE-------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Research Assistant}{August 2024 -- May 2025}
      {Tarleton State University}{Stephenville, TX}
      \resumeItemListStart
        \resumeItem{Contributed to the development of a model written in C and CUDA to visualize data.}
        \resumeItem{Presented research findings at academic conferences and seminars.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Bioinformaticist}{May 2024 -- February 2025}
      {Texas A\&M Agrilife}{Stephenville, TX}
      \resumeItemListStart
        \resumeItem{Implemented Bash scripts to automatize analyzing DNA sequence reads using terminal-based bioinformatics tools.}
        \resumeItem{Built and managed multiple lab computers and ensured accuracy and integrity of sequencing for publication results.}
      \resumeItemListEnd

    \resumeSubheading
      {Patient Access Specialist}{February 2023 -- Present}
      {Surepoint - Emergency Center}{Stephenville, TX}
      \resumeItemListStart
        \resumeItem{Primary contact for patients entering the ER. This included using a customer relationship management system.}
        \resumeItem{Processed and organized patient records using electronic health record systems, and managed financial transactions.}
      \resumeItemListEnd

    \resumeSubheading
      {Acting Center Management}{October 2021 -- January 2023}
      {Mathnasium}{Hurst, TX}
      \resumeItemListStart
        \resumeItem{Management experience at tutoring facility  K-12.}
      \resumeItemListEnd

    
    \resumeSubheading
      {Cybersecurity Intern}{April 2025 -- Present}
      {RedKnight}{Mineral Wells, TX}
      \resumeItemListStart
        \resumeItem{Created documentation to guide interns in effectively using common security tools and software.}
        \resumeItem{Deployed virtual machines on the network to simulate traffic for the in-house intrusion detection system (IDS).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%------------PROJECTS------------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{N-Body Simulations of Microplastic Removal Using Polymers} $|$ \emph{C, CUDA}}{August 2024 -- May 2025}
          \resumeItemListStart
            \resumeItem{Co-developed and optimized a CUDA-based N-body simulation of microplastic-polymer interactions with real-time 3D visualization using OpenGL, boosting performance and user engagement.}
            \resumeItem{Helped design an interface and collaborated with a team to align the tool with project goals and user needs.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Capstone - Botnet Traffic Detection Analysis Program} $|$ \emph{Python}}{January 2025 -- May 2025}
          \resumeItemListStart
            \resumeItem{Co-developed a PyQt6-based GUI application for botnet detection using machine learning and neural networks on the CTU-13 dataset.}
            \resumeItem{Improved usability and accessibility by integrating a PyQt6 GUI for dataset upload, algorithm selection, training, and real-time analysis.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING/Technical SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, Bash} \\
     \textbf{Developer Tools}{: Git, Visual Studio, Linux, VS Code} \\
     \textbf{Libraries}{: Cryptography, Sklearn, Matplotlib, NumPy, Pandas, PyQt6, CUDA} \\
     \textbf{Personal}{: Communication, IT foundation, documentation, willingness to learn} \\
    }}
 \end{itemize}


%------------Certifications------------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Basic Life Support(BLS)}{  Expires: February 2027} \\
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Tarrant County Community College \textnormal{- GPA: 4.0}}{Hurst, TX}
      {}{August 2021 -- December 2022}
      \resumeItemListStart
        \resumeItem{36 credit hours completed}
        \resumeItem{Phi Theta Kappa (honor society)}
        \resumeItem{Vice president of award winning Chemistry Club and treasurer of the Infinity Math Club}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tarleton State University \textnormal{- GPA: 3.84}}{Stephenville, TX}
      {}{Janurary 2023 -- May 2025}
      \resumeItemListStart
        \resumeItem{B.S. in Cybersecurity, minor in mathematics}
        \resumeItem{Vice President of Tarleton Mathematics Club and Vice President of Tarleton Computer Society}
        \resumeItem{Notable Achievements: President's List 3 times; Tarleton RIED Symposium 1st Place 2025, Capstone 3rd Place}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}